%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Projects}

\begin{cventries}
	%---------------------------------------------------------
	\cventry
	{
		M.Sc. Thesis Project [Score: 19.75/\textbf{20}]
		\newline
		Under supervision of Dr. Mahdieh Soleymani Baghshah
	}
	{Conditional Text Generation with Neural Networks}
	{2019}{Sharif University}
	{
        The goal of this project was to generate sentences with desired labels such as sentiment or any other categorical label. To have complete control over the output of the model (with greedy decoding), the "(Single) Latent Based Models" were selected which VAE is one of the most popular ones. To overcome the "KL Collapse" problem or in simple words, the latent ignorance problem of VAE in Language Modeling task, the "Wasserstein Autoencoder" was replaced. At last to learn the latent space of sentences of each label value, a conditional "Masked Autoregressive Flow" network which is a Flow-Based Network was taken into account.
	}
	%---------------------------------------------------------
	\vspace{0.6cm}
	%---------------------------------------------------------
	\cventry
	{
        B.Sc. Thesis Project [Score: 19/\textbf{20}]
        \newline
        Under supervision of Prof. Mohammad Mehdi Homayounpour
    }
	{Voice Search Engine on Persian Poems}
	{2017}{Amirkabir University}
	{
        Our main goal in this project was to detect a read poem while a Phoneme to Grapheme model and the text of a wide range of Persian poems were given to me. To this end, I trained a Word to Grapheme model and designed a heuristic search to match the sequence of read graphemes with the sequence of poem graphemes and find some candidates, and at last calculating minimum edit distance to find the nearest poem. This project was implemented in a Client-Server manner. The server was based on Django python framework and the Client was an Android app.
	}
	%---------------------------------------------------------
	\vspace{0.6cm}
	\cventry
	{Research at AUTMAN (AUT-Uofm)}
	{Locating Humanoid Robots in Football Field}
	{2016}{Amirkabir University}
	{
        Our main problem in AUTMAN was to locate the robot in the field of play based on observations that got from the camera on its head. My primary task was to study the localization methods, especially the Particle Filter method. It was implemented in collaboration with my other teammates.
	}
	%---------------------------------------------------------
\end{cventries}

\cvsection{Notable Course Projects}

\begin{cvhonors}
    	%---------------------------------------------------------
        \cvhonor
        {Design and implementation of Image2Latex model; Learn to convert an image of a mathematical formula to corresponding latex code.}
        {Deep Learning Course}
        {}{2019}
        %---------------------------------------------------------
    
	%---------------------------------------------------------
	\cvhonor
	{MAP and Bayesian Training of a Recommender System}
	{Probabilistic Graphical Models Course}
	{}{2018}
	%---------------------------------------------------------
	%---------------------------------------------------------
	\cvhonor
	{Design and Implementation of Smart Agents for Pacman Game}
	{Artificial Intelligence Course}
	{}{2017}
	%---------------------------------------------------------
	%---------------------------------------------------------
	\cvhonor
	{Design and implementation of a 2D Strategic Multiplayer Game with JAVA}
	{Advanced Programming Course}
	{}{2013}
	%---------------------------------------------------------
\end{cvhonors}

